Argennon: A Scalable Smart Contract Platform

### 2021-06-25 tex/sections/consensus.tex
Add the reserve delegates concept
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

There is two primary types of certificate committees in Argennon: the committee of \emph{delegates} and the committee
of \emph{validators}. Argennon has one committee of delegates and $m$ committees of validators.

The committee of delegates generates a certificate for every block of the Argennon blockchain, and each
committee of validators generates a certificate every $m$ blocks. A validators' committee will
certify a block only if it has already been certified by the committee of delegates and every committee
generates a certificate for a different block. A block is considered
final only after it gets a certificate from both of these committees.

@@

The committee of delegates is a small committee of trusted delegates, elected by Argennon users either through the
Argennon Decentralized Autonomous Governance system (ADAGs\footnote{pronounced \textipa{/eI-dagz/}.}) or by emergency
voting during the recovery protocol. At the start of the Argennon mainnet, this committee will have
five members, and later its size could be changed by the ADAGs in a procedure described
in Section~\ref{ch:governance}.

@@

Usually, the delegates are large organizations, and they have enough computational resources to generate blocks
very fast. However, a block is not completely final if it does not have the certificate of the validators' committee.
A certified block by the delegates will not be accepted by the network, if the last block certified by
the validators is behind it more than a certain number of blocks.

@@

\subsection{The Committee of Validators}\label{subsec:validators-committee}

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system. This value is measured in ARGs. Every $n$ block randomly $m$ committees are selected from
accounts whose stake value is higher than \texttt{minValidatorsStake} threshold. This
threshold is determined by the ADAGs, but it can never be higher than $100$ ARGs.
These committees are chosen in a
way that the total stake of members of each committee is approximately equal and every account is a member of
\textbf{at least} one committee.

Every member of a validators' committee has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is a part of the staking database. A validator can change
his status through a method invocation
from this smart contract. When an account sets its status to \texttt{offline}, it receives a small reward, and
it can not change it back to \texttt{online} for \texttt{statusCoolDown} number of blocks.

@@

A block certificate issued by some members of a validators' committee is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} members is higher than \texttt{minOnlineStake} percent of the
    total stake of all members. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of committee members that have \texttt{online} status.
\end{itemize}

If the total online stake of a committee goes lower than \texttt{minOnlineStake} threshold, nodes initiate the recovery
consensus protocol.

As we mentioned before, every block of the Argennon blockchain needs a certificate from a specific committee of
validators, which repeats every $m$ blocks. To decide about signing the block certificate, an honest member of a
validators' committee checks the conditional validity of the committee block, and if the block is valid he issues
an "accept" signature, otherwise he issues a "reject" signature.

block certificates issued by validators' committees are included in the Argennon blockchain. A block may contain
multiple certificates, provided that those certificates belong to consecutive blocks.

@@

If a committee of validators, at any point issues a "reject" certificate for a block, the network will initiate the
recovery protocol.

@@

\subsection{The Recovery Protocol}\label{subsec:recovery}
\note{not yet written...}

\subsection{Analysis}\label{subsec:consensus-math}
\note{not yet written...}

>>>>

There are two primary types of certificate committees in Argennon: the committee of \emph{delegates} and the committee
of \emph{validators}. Argennon has one committee of delegates and $m$ committees of validators.

The committee of delegates generates a certificate for every block of the Argennon blockchain, and each
committee of validators generates a certificate every $m$ blocks. A validators' committee will
certify a block only if it has already been certified by the committee of delegates. Every committee of validators has
an index between $0$ and $m - 1$, and it issues a certificate for block number $n$, if $n\mod m$ equals
the committee index.

A block is considered final only if it has a valid certificate from both the delegates and the
validators. A valid certificate from validators could be either a valid certificate from the committee of
validators with the appropriate index or a certificate from all the validators.

@@

The committee of delegates is a small committee of trusted delegates, elected by Argennon users either through the
Argennon Decentralized Autonomous Governance system (ADAGs\footnote{pronounced \textipa{/eI-dagz/}.}) or by emergency
voting during the recovery protocol. At the start of the Argennon mainnet, this committee will have
five members, and later its size could be changed by the ADAGs in a procedure described
in Chapter~\ref{ch:governance}.

@@

Besides the main delegates' committee, a reserve committee of delegates consists of three members is elected by users
through the ADAGs. In case the main committee fails to generate new blocks or behaves maliciously, the task of
block generation will be assigned to the reserve committee until a new main delegates' committee is elected
through the ADAGs.

Usually, the delegates are large organizations, and they have enough computational resources to generate blocks
very fast. However, a block is not completely final if it does not have the certificate of the validators.
A certified block by the delegates will not be accepted by the network, if the last block certified by
the validators is behind it more than a certain number of blocks.

@@

\subsection{Validators}\label{subsec:validators-committee}

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system, and is measured in ARGs. Any account whose stake value s higher than
\texttt{minValidatorsStake} threshold is considered a validator.
The \texttt{minValidatorsStake}
threshold is determined by the ADAGs, but it can never be higher than $100$ ARGs.

Every $n$ blocks randomly $m$ committees are selected from
validators, in a way that the total stake of members of each committee is approximately equal and every
account is a member of \textbf{at least} one committee.

Every member of a validators' committee has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is a part of the staking database. A validator can change
his status through a method invocation
from the ARG smart contract. When an account sets its status to \texttt{offline}, it receives a small reward, and
it can not change it back to \texttt{online} for \texttt{statusCoolDown} number of blocks.

@@

A block certificate issued by some members of a validators' committee is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} members of the committee is higher than \texttt{minOnlineStake} percent
    of the total stake of all members. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of committee members that have \texttt{online} status.
\end{itemize}

If the total online stake of a committee goes lower than \texttt{minOnlineStake} threshold, a partial reshuffling
of committee members will be performed by the protocol in order to move some online members to the committee without
enough online stake. If the reshuffling can not solve the problem, nodes will initiate the recovery consensus
protocol.

As we mentioned before, every block of the Argennon blockchain needs a certificate from a specific committee of
validators. To decide about signing the block certificate, an honest member of a
validators' committee checks the conditional validity of the committee block, and if the block is valid he issues
an "accept" signature, otherwise he issues a "reject" signature.

block certificates issued by validators' committees are included in the blocks of the Argennon blockchain.
A block can contain multiple certificates, provided that those certificates belong to consecutive blocks.

@@

If a committee of validators, at any point issues a "reject" certificate or does not issue a certificate for its
block, after \texttt{certificateTimeOut} period of time,
nodes will initiate the recovery protocol.

@@

\subsection{The Recovery Protocol}\label{subsec:recovery}
\note{not yet written...}
%
%Validators stop issuing certificates for normal blocks and they will only issue certificates for \emph{statuts} blocks.
%A status block is a special block which can only contain status change transactions. Status blocks need to be
%certified by all the validators.
%all online validators will check the
%validity of that block. if they do not issue a certificate for that black either
\subsection{Analysis}\label{subsec:consensus-math}
\note{not yet written...}
